\documentclass[letterpaper,11pt]{article}


\usepackage[scaled=0.9]{helvet} % Scale Helvetica font to 90% of its original size
\renewcommand{\familydefault}{\sfdefault}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{multicol}
\input{glyphtounicode}

\definecolor{navyblue}{RGB}{0, 0, 128}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in} % Adjust left margin
\addtolength{\evensidemargin}{-0.5in} % Adjust right margin for even pages
\addtolength{\textwidth}{1in} % Increase text width
\addtolength{\topmargin}{-0.7in} % Adjust top margin
\addtolength{\textheight}{1.0in} % Increase text height

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in} % Set table column separation to zero

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\renewcommand{\textbf}[1]{{\fontseries{sb}\selectfont #1}}  % medium
%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-2.5pt}}  % Adjust spacing after each resume item (affects items under experience/projects)
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item % Space before each subheading (affects each position under experience)
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt} % Space after each subheading (affects the overall height of the section)
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7.5pt} % Space after each sub-subheading
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt} % Space after each project heading
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3.8pt}} % Space after each sub-item

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}} % Space after item list (affects the spacing below lists)

% New command for the technical skills table
\newcommand{\skill}[2]{
  \textbf{#1:} #2
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\fontsize{34}{34}\selectfont\textbf{\scshape\textcolor{NavyBlue}{Kushagra Agrawal}}}\\[1pt]
    \normalsize
    +91-8871267879 \hspace{2pt} $|$ \hspace{2pt} 
    \href{mailto:kush78799@gmail.com}{\textcolor{NavyBlue}{\textbf{kush78799@gmail.com}}} \hspace{2pt} $|$ \hspace{2pt} 
    \href{https://www.linkedin.com/in/ayyekush/}{\textcolor{NavyBlue}{\textbf{LinkedIn}}} \hspace{2pt} $|$ \hspace{2pt}
    \href{https://github.com/ayyekush}{\textcolor{NavyBlue}{\textbf{GitHub}}}
\end{center}

% \vspace{1pt} 
%-----------PROFESSIONAL SUMMARY-----------
\large\section{\textcolor{NavyBlue}{\textbf{Professional Summary}}}
\resumeSubHeadingListStart
  \resumeItem{
    Aspiring Machine Learning Engineer and Data Scientist with a practical, hands-on approach to learning and building. Passionate about Artificial Intelligence, Full Stack Web Development, Web Automation, and Ethical Hacking. Proficient in Deep Learning, NLP, Frontend/Backend development, and deployment of intelligent web applications.
  }
\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------

\large\section{\textcolor{NavyBlue}{\textbf{Technical Skills}}}
\begin{tabular}{p{0.46\textwidth}@{\hspace{1.5em}}p{0.46\textwidth}}
\skill{ML/AI Frameworks}{Scikit-learn,TensorFlow,Keras, OpenCV} & \skill{Cloud Platforms}{Google Cloud Platform (basics), Telegram Bot API} \\[4pt]
\skill{Programming}{Python, C++, Java, JavaScript, SQL, Bash}  & \skill{Automation \& Scripting}{Selenium, cron (macOS), Ngrok, Bash, virtualenv, threading \& asyncio)}  \\[4pt]
\skill{Web Development}{HTML/CSS/JS, Express.js, Node.js, EJS, Axios, Multer} & \skill{Databases}{MySQL, MongoDB}  \\[4pt]
\skill{Deployment}{FastAPI, Flask,Jinja, Streamlit, Docker (basics)} &
\skill{Visualization}{Matplotlib, Seaborn}  \\[4pt]
%  \\[4pt]
% \skill{Automation}{MySQL, MongoDB, ChromaDB} & \skill{Visualization}{Matplotlib, Seaborn} \\[4pt]
\end{tabular}

\vspace{2pt}

\begin{tabular}{p{0.97\textwidth}}
\end{tabular}

%-----------PROJECTS-----------
\large\section{\textcolor{NavyBlue}{\textbf{Projects}}}
  \resumeSubHeadingListStart
\resumeProjectHeading
  {\large\textbf{{\href{XXXgithub}{\textbf{NLP Model Benchmarking Dashboard}}}} $|$ \emph{Scikit-learn, TensorFlow-Keras, Jinja2/CSS/JS}}
  {\href{XXXlivelink}{\textit{\textcolor{NavyBlue}{LiveLink}}} $|$ \href{XXXgithub}{\textit{\textcolor{NavyBlue}{GitHub}}}}
  \resumeItemListStart
    \resumeItem{A comprehensive NLP web app that compares and benchmarks 6+ different ML-NLP models like LogReg, SVM, Naive Bayes, and Neural Networks on book reviews.}
    \resumeItem{Vectorization techniques such as BagofWords and TFIDF used for thorough comparison and analysis.}
    \resumeItem{Built on FastAPI backend and Jinja2-powered frontend dashboard for real-time predictions.}
  \resumeItemListEnd
\resumeProjectHeading
    {\large\textbf{{\textbf{Digit Dash – Digit Recognition Game}}} $|$ \emph{CRNN, TensorFlow, Docker, GCP}}
    {\href{XXXlivelink}{\textit{\textcolor{NavyBlue}{LiveLink}}} $|$ \href{XXXgithub}{\textit{\textcolor{NavyBlue}{GitHub}}}}
    \resumeItemListStart
        \resumeItem{A Game where users Draw digits that are tested using CRNN model trained on hand-written digits.}
        \resumeItem{FastAPI backend serves real-time predictions; app containerized with Docker and deployed on Cloud Run}
    \resumeItemListEnd
\resumeProjectHeading
  {\large\textbf{{\textbf{Amazon Review Scraper \& Analyzer}}} $|$ \emph{Selenium, NLP}}
  {\href{XXXlivelink}{\textit{\textcolor{NavyBlue}{LiveLink}}} $|$ \href{XXXlivelink}{\textit{\textcolor{NavyBlue}{GitHub}}}}
  \resumeItemListStart
    \resumeItem{Web application that automatically scrapes and analyzes given Amazon product reviews in Real-Time.}
    \resumeItem{Implemented sentiment analysis models with NLP to predict review sentiment and generated word clouds for visualization.}
    \resumeItem{Created both fast and slow humanoid-like scraping modes to avoid detection while collecting product feedback data.}
  \resumeItemListEnd
\resumeProjectHeading
{\large\textbf{{\textbf{TrafficSignAI – Intelligent Traffic Sign Classifier}}} $|$ \emph{CRNN, PIL, Keras, Computer Vision}}
{\href{XXXlivelink}{\textit{\textcolor{NavyBlue}{LiveLink}}} $|$ \href{XXXgithub}{\textit{\textcolor{NavyBlue}{GitHub}}}}
  \resumeItemListStart
    \resumeItem{Convolutional Neural Network Model that classifies 57 different traffic sign in real-time.}
    \resumeItem{Integrated model with a FastAPI backend to serve predictions via image uploads and public URLs.}
    \resumeItem{Enabled live contrast enhancement, resizing, and pre-processing of grayscale images to boost model accuracy.Potential applications include driver-assistance systems and autonomous vehicles.}
  \resumeItemListEnd


  
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\large\section{\textcolor{NavyBlue}{\textbf{Certifications}}}
\begin{itemize}
    \setlength{\itemsep}{-0.4em}
    \setlength{\parsep}{0em}
    \setlength{\topsep}{0em}
    \item Supervised Machine Learning: Regression and Classification — Stanford University 
    \hfill \textbf{\href{https://coursera.org/verify/ZMTBQVXRZZZD}{\textcolor{NavyBlue}{Certificate Link}}}
    
    \item Neural Networks and Deep Learning — DeepLearning.AI 
    \hfill \textbf{\href{https://coursera.org/verify/Q6MCJFVXQ9EN}{\textcolor{NavyBlue}{Certificate Link}}}

    \item Complete Data Science, Machine Learning, Deep Learning, NLP Bootcamp — Udemy
\end{itemize}

%-----------EDUCATION-----------
\large\section{\textcolor{NavyBlue}{\textbf{Education}}}
\resumeSubHeadingListStart
  \resumeSubheading
    {Institute of Engineering and Technology, DAVV}{Indore}
    {Bachelor of Engineering - Information Technology}{Aug 2023 – Present}
    
  \resumeSubheading
    {Kendriya Vidyalaya, Pachmarhi}{Madhya Pradesh}
    {Senior Secondary (CBSE) – PCM; Scored 94.8\%}{2022}

\resumeSubHeadingListEnd


\end{document}